---
title: "NormalDistribution"
format: html
editor: visual
---

## Normal Distribution

Find a) Less than 15 minutes

```{r}
m = 20
sd = 5
pnorm(15, m, sd)
```

b\) More than 25 minutes

```{r}
p2 = pnorm(40, mean = 20, sd = 5) - pnorm(25, mean = 20, sd = 5)
p2
```

c\) Between 15 and 25 minutes

```{r}
p3 = pnorm(25, m, sd) - pnorm(15, m, sd)
p3
```

d\) Plot the distribution

```{r}
x = seq(0, 40)
y = dnorm(x, mean = 20, sd = 5)
plot(x, y, type = 'l', xlab = "minutes", ylab = "probability", main = "Normal Distribution curve")

# plotting part a)
x2 = seq(0,15)
y2 = dnorm(x2, mean = 20, sd = 5)
polygon(c(0, x2, 15), c(0, y2, 0), col = 'orange')

# plotting part b)
x3 = seq(25, 40)
y3 = dnorm(x3, mean = 20, sd = 5)
polygon(c(25, x3, 40), c(0, y3, 0), col = 'green')

# plotting part c)

x4 = seq(15, 25)
y4 = dnorm(x4, mean = 20, sd = 5)
polygon(c(15, x4, 25), c(0,y4,0), col = 'blue')
```

e\) Table the distribution

```{r}

```

## Question 1

mean = 1500, sd = 350

a\) \< 750 games

```{r}
m = 1500
sd = 350

p1 = pnorm(750, m, sd)
p1
```

b\) more than 2000 games

```{r}
p2 = 1 - pnorm(2000, m, sd)
p2
```

c\) find the 90th percentile of the number of games played during career

```{r}
p90 <- qnorm(0.90, mean = m, sd = sd)
p90
```

## Question 2

Find the probability of a specific range of values, such as calculating that penguin flipper lengths(mm,mm) are less than 200mm which is approx 84 percent in this case

```{r}
m <- 192.9
sd <- 7.1

# P(X < 200)
pnorm(200, mean = m, sd = sd)
```
